Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-07 paper/paper.tex
Muck around with plotting some more, starting to like this

    \caption{Cumulative performance. The parallel versions, dotted, are always better in aggregate
    than the sequential versions, solid.}
\end{figure*}

\begin{figure*}[tb]
    \includegraphics*{gen-graph-as-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33v.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33ved.pdf}

@@

    \includegraphics*{gen-graph-as-plain-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-as-33ve-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-as-sip.pdf}
\end{figure*}

% \begin{figure*}[tb]
%     \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Per-instance speedups. The $x$-axis is sequential performance and the $y$-axis is 32
%     threaded performance, so points below the diagonal line represent a speedup.}
% \end{figure*}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t2-vs-clique-par-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t4-vs-clique-par-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t8-vs-clique-par-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-par-t16-vs-clique-par-t32.pdf}
% 
%     \caption{Scalability and reproducibility, clique algorithm.}
% \end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t2-vs-clique-cilk-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t4-vs-clique-cilk-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t8-vs-clique-cilk-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t16-vs-clique-cilk-t32.pdf}
% 
%     \caption{Scalability and reproducibility, clique algorithm, Cilk.}
% \end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t2-vs-mcsplit-par-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t4-vs-mcsplit-par-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t8-vs-mcsplit-par-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t16-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Scalability and reproducibility, McSplit algorithm.}
% \end{figure}

>>>>

    \caption{The cumulative number of instances solved over time, for different families and
    algorithms. The 32 threaded parallel versions (shown using dotted lines) are always better in
    aggregate than the sequential versions (shown using solid lines).}
\end{figure*}

% \begin{figure*}[tb]
%     \includegraphics*{gen-graph-as-plain.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33v.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33ved.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-as-plain-connected.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-33ve-connected.pdf}
%     \hfill
%     \includegraphics*{gen-graph-as-sip.pdf}
% 
%     \caption{Aggregate speedups.}
% \end{figure*}

\begin{figure*}[tb]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-connected-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ve-connected-clique-vs-clique-par-t32.pdf}

@@

    \includegraphics*{gen-graph-histogram-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-plain-connected-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33ve-connected-clique-vs-clique-par-t32.pdf}

    \caption{On the top row, per-instance speedups, using the clique algorithm. The $x$-axis is
    sequential performance and the $y$-axis is 32 threaded performance, so points below the diagonal
    line represent a speedup. Darker points represent instances where the solution is relatively
    large compared to the order of the input graphs. Below, histograms plotting the distribution of
    speedups for instances whose sequential runtime was at least 500 milliseconds, and below the
    timeout.}
\end{figure*}

\begin{figure}[tb]
    \hfill
    \includegraphics{gen-graph-as-clique.pdf}
    \hfill

    \caption{Aggregate speedups from the clique algorithm using 32 threads, for each supported
    family of instances.}
\end{figure}

% \begin{figure*}[tb]
%     \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Per-instance speedups. The $x$-axis is sequential performance and the $y$-axis is 32
%     threaded performance, so points below the diagonal line represent a speedup.}
% \end{figure*}
% 
\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t2-vs-clique-par-t4.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-par-t4-vs-clique-par-t8.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t8-vs-clique-par-t16.pdf}

    \includegraphics*{gen-graph-scatter-33ved-clique-par-t16-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}

    \caption{Per-instance speedups from the clique algorithm on vertex- and edge-labelled, directed
    instances, when going from sequential to two threads in the first plot, then increasing the
    number of threads in subsequent plots. The final plot shows 32 threads versus a repeated run
    also with 32 threads.}
\end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t2-vs-clique-cilk-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t4-vs-clique-cilk-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t8-vs-clique-cilk-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t16-vs-clique-cilk-t32.pdf}
% 
%     \caption{Scalability and reproducibility, clique algorithm, Cilk.}
% \end{figure}
% 
% \begin{figure}[tb]
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t2-vs-mcsplit-par-t4.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t4-vs-mcsplit-par-t8.pdf}
% 
%     \vspace*{1em}
% 
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t8-vs-mcsplit-par-t16.pdf}
%     \hfill
%     \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t16-vs-mcsplit-par-t32.pdf}
% 
%     \caption{Scalability and reproducibility, McSplit algorithm.}
% \end{figure}
